Capture and Replay Tools in the Field

### 2017-04-27 paper.tex
Added future additions section

\subsubsection{Client Side}

\subsubsection{Server Side}

\section{Future Additions to Reanimator}

\subsection{Developer Interface on Playback}

\subsection{Synchronize Only Changes}

\subsection{Smaller Upload Size}

>>>>

\subsubsection{Client Side}
We refer to the Reanimator JavaScript code as the client side because it is running locally on the web client’s machine. To enable log uploading, we modified the capture function in the core.js file. We added parameters so the user could pass in a boolean to enable uploading, and so the client could pass in a UUID to be associated with the log. A UUID, or Universally Unique Identifier, is a unique ID for the client. Generation and use of UUIDs is outlined in RFC 4122. \cite{p.leachm.meallingr.salz2005}
\par
The client, if log uploading is enabled, will upload the log to an HTTP POST service every five seconds. By default, we programmed Reanimator to POST to a file called reanimator.php in the same directory as the JavaScript file.
\par
We duplicated and extended the original tile game demo to support uploading to a webservice. A user can play the tile game, then can select a list of sessions from a dropdown. After selection, he or she can see any past game that was logged to the server.

\subsubsection{Server Side}
The server can be written any way the developer prefers as long as it accepts HTTP POST requests.
\par
We included a sample HTTP POST web service file in the dist directory of Reanimator. The simple script is written in PHP and will upload the logs to a MySQL database for retrieval later. It will overwrite any old logs with the same UUID.
\par
We also included a sample database configuration file with the uploading tile game demo. Because a developer should know how to setup a simple web service and MySQL server, we do not feel the need to explain them in detail.

\section{Future Additions to Reanimator}
In the future, we recommend adding more features to Reanimator. We believe that it is useful to developers after our additions, but could be improved further.

\subsection{Developer Interface on Playback}
We propose creating a developer interface, or developer portal. It would provide a user friendly way for developers to organize and replay their captured sessions. The interface could include a play/pause button, and let the developer choose the speed to play back the session.
\par
Because this does not add any core functionality, but rather an improved user experience, we recognize that it would help developers but we did not choose to implement it during our Reanimator extension/proof of usefulness test.

\subsection{Synchronize Only Changes}
Our demonstration implementation will upload the user's log every five seconds. The server code will simply overwrite the log data for that user in the database when it receives new data. This practice is fine for demo purposes and for small websites, but is obviously not scalable to large websites. We propose uploading only the changes of the log to the server.
\par
To ensure that data is not lost, we could allow the server to respond to the POST request to tell the client if the log upload was successful. The client would keep track of successful log pushes and would know if it needs to retry or if it can upload a new section of the log.
\par
This modification would appear small to each client, but would be a huge difference to large websites which could potentially be receiving many log pushes at the same time.

\subsection{Smaller Upload Size}
The log files that Reanimator generates are large relative to the usefull information that they contain. The files contain every piece of information about the layout of the webpage. We propose modifying the way that logs are stored. There will be one initial log with the entire DOM, but subsequent events will simply be a changelog of the original log file.
\par
This would make the entire log smaller, allowing for smaller uploads and less memory used at the client.
\par
It is important to note that this solution is different from the previous suggestion (synchronizing only the changes). The entire log would be much smaller, as it would only contain the changes to the original log file. We can combine this with the previous suggestion to further minimize the overhead of Reanimator.
